---
title: "Machine Learning Overview"
subtitle: "Applied Machine Learning"
author: "Jameson > Hendrik > Calvin"
format: 
    revealjs: 
        theme: night
        mainfont: monospace
        slide-number: true
        show-slide-number: all
        width: 1050
        height: 700

execute:
    echo: true
    freeze: true  # never re-render during project render

project:
  execute-dir: project
---


## Agenda

1. Course Overview
2. Review of Regression
3. Dinner Break
4. Classification and Ethics
5. Basic Feature Engineering
6. Vocabulary

# Course Overview

## Expectations and assignments

1. Homework assignments
2. Exams
3. Modeling Project
4. Course Policies
5. My expectations for you

# Introductions

## About me
- BS in mathematics
- PhD in pure mathematics (2015 I think?)
- Taught liberals arts college math in the Netherlands
- Several quant and modelling roles in banking, most recently 
- Model bureaucrat / manager

## About you?
  - Background
  - Goals for this program and/or course

## Basic concepts in Machine Learning

- What is a data scientist?
- What is machine learning? 
- What is the role of judgment in machine learning?
- What are the differences between machine learning, statistics and econometrics?
- When is "mere" correlation enough? When is it not?

# Review of Regression

## Setup

```{r}
library(tidyverse)
library(moderndive)
theme_set(theme_dark())
library(thematic)
thematic_rmd(bg = "#111", fg = "white")
wine_all = readRDS("../../dat/wine.rds")
wine = wine[sample(nrow(wine), 100), ]
```

## Single Variable

```{r}
library(moderndive)
wine <- wine %>% 
  mutate(bordeaux=(province=="Bordeaux"))
m1 <- lm(price ~ points, data = wine)
get_regression_table(m1)
```
## Let's draw it

```{r}
ggplot(wine_gg, aes(x = points, y = price)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  labs(title = "Regression of Price on Points",
       x = "Points",
       y = "Price")
```