% Don't touch this %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage[left=1in,top=1in,right=1in,bottom=1in,headheight=3ex,headsep=3ex]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{quoting}

\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

\newcommand{\blankline}{\quad\pagebreak[2]}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Modify Course title, instructor name, semester here %%%%%%%%

\title{CS-152: Data Structures}
\author{Calvin Deutschbein (they)}
\date{Willamette University, Spring	 2024}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't touch this %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[sc]{mathpazo}
\linespread{1.05} % Palatino needs more leading (space between lines)
\usepackage[T1]{fontenc}
\usepackage[mmddyyyy]{datetime}% http://ctan.org/pkg/datetime
\usepackage{advdate}% http://ctan.org/pkg/advdate
\newdateformat{syldate}{\twodigit{\THEMONTH}/\twodigit{\THEDAY}}
\newsavebox{\MONDAY}\savebox{\MONDAY}{Mon}% Mon
\newcommand{\week}[1]{%
%  \cleardate{mydate}% Clear date
% \newdate{mydate}{\the\day}{\the\month}{\the\year}% Store date
  \paragraph*{\kern-2ex\quad #1, \syldate{\today} - \AdvanceDate[4]\syldate{\today}:}% Set heading  \quad #1
%  \setbox1=\hbox{\shortdayofweekname{\getdateday{mydate}}{\getdatemonth{mydate}}{\getdateyear{mydate}}}%
  \ifdim\wd1=\wd\MONDAY
    \AdvanceDate[7]
  \else
    \AdvanceDate[7]
  \fi%
}
\usepackage{setspace}
\usepackage{multicol}
%\usepackage{indentfirst}
\usepackage{fancyhdr,lastpage}
\usepackage{url}
\pagestyle{fancy}
\usepackage{hyperref}
\usepackage{lastpage}
\usepackage{amsmath}
\usepackage{layout}

\lhead{}
\chead{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Modify header here %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\rhead{\footnotesize Data Structures}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Don't touch this %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lfoot{}
\cfoot{\small \thepage/\pageref*{LastPage}}
\rfoot{}

\usepackage{array, xcolor}
\usepackage{color,hyperref}
\definecolor{clemsonorange}{HTML}{EA6A20}
\hypersetup{colorlinks,breaklinks,linkcolor=clemsonorange,urlcolor=clemsonorange,anchorcolor=clemsonorange,citecolor=black}

\begin{document}

\maketitle

\blankline

\begin{tabular*}{.93\textwidth}{@{\extracolsep{\fill}}lr}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Modify information %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
E-mail: \texttt{ckdeutschbein@willamette.edu} & Web: \href{https://cd-public.github.io/courses/data_structures/241f21.html}{\tt\bf cd-public.github.io/}  \\

 Office Hours: By Appt. \& TBA  &  Lecture MWF 9:10-10:10 PM \\

 Office: Zoom, Ford 206 & Lecture Hall: "Salem TBD" \\
 & \\
\hline
\end{tabular*}

\vspace{5 mm}

% First Section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Course Description}

Theoretical and practical study of programming and abstract data types including lists, stacks, queues, trees and algorithms used on these data structures. The course includes object implementation of structures and sharpens programming skills learned in previous courses.

A note: while this course may be of interest to majors in Data Science, this course's name reflects a more traditional usage of the term "data", simply referring to information stored in computer memory. It also called "Discrete Structures" or "Programming Abstractions" at other colleges and universities. 
% Second Section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Required Materials}

Required materials will be available on the \href{https://cd-public.github.io/courses/strs24}{course webpage}.


% Third Section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Prerequisites}

This class is meant for computer science students who have completed introductory coursework in programming. Be comfortable with the content of CS 151 or equivalent.
\section*{Accessability}

I will make every effort to ensure all coursework and materials are accessible to all students, including working with on-campus specialists. However, there is always room for improvement. I always appreciate hearing from students about how I can make the course more accessible, so please reach out if there is something I can be doing better!

% Fourth Section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Course Objectives}
This course will teach you how to organize the data used in computer programs so that manipulation of that data can be done efficiently on large problems and large data instances.  This course will address both how to use the data structures found in the libraries of programming languages, and how those libraries are constructed and why the items that are included in them are there (and why some are excluded). 
\begin{itemize}
\item Study important categories of problems that are commonly encountered in software development
\item Learn data organizations to practically and efficiently solve problems. 
\item Analyze the performance and efficiency of your algorithms preceding the upper level course in algorithms. 
\item Encoding data organizations in Python programs. 
\item Practice program and software organization.
\item See examples of the induction proof methods to reason about your programs supporting mid level courses in mathematics.  
\end{itemize}
Competency of the data structures taught in this course will prepare you to study more advanced topic areas where those data structures are heavily used: operating systems, networking, graphics, vision, compilers, databases, and security.

% Fifth Section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Course Structure}

The course will be composed of lectures, homeworks, midterms, and a final project.

\subsection*{Lecture Structure}

Lectures are scheduled for Mondays, Wednesdays, and Fridays at 9:10 A.M. in "Salem TBD". The schedule
of lectures will be available on the \href{https://cd-public.github.io/courses/strs24}{course webpage}.

\bigskip
\noindent I will combine lectures with slides, live coding demonstrations, and in-class exercise. Slides will be posted, and code from the demonstrations will be posted, but intermediate coding stages may not be captured. 

\subsection*{Homework Structure}

Feedback will be provided on homework assignments. Homework assignments will be considered when determining grades for this course.

\bigskip
\noindent Homeworks will consist of programming assignments to be completed outside of class and submitted
for feedback. There will be a ``Homework 0'' at the beginning of the semester to get used to
programming and assignment submission. Homework assignments be out of either 50 or 100 points, for a total of 500 points.
Your grade will be determined based on your performance on the best 400 points worth of assignments - this is roughly equivalent
to dropping the lowest homework grade out of five assignments.

\bigskip
\noindent Homework assignment will be due at 9:10 A.M. on Fridays so we can discuss solutions in class on the 
day they are due.

\bigskip
\noindent As a rule, I encourage students to submit their assignment as-is at the due date and not to
submit late work. By way of explanation, it is my experience as both a student and a grader that time spent working on assignments after their deadline is often better spent working on the next assignment.

\bigskip
\noindent As-is submission is supported in the grading policy by dropping the lowest homework
grade. In special circumstances such as extended medical problems or other unforeseeable
emergencies, please reach out and so we can collaboratively develop a more personal
solution to achieve the learning objectives of the course.
\bigskip
\noindent Homework assignments will be assessed by an autograder that will be provided with the assignment, so you can assess your progress on the assignment prior to receiving my feedback.

\subsubsection*{Midterm Structure}

Feedback will be provided on midterm exams.  Midterm exams will be considered when determining grades for this course.

\bigskip
\noindent There will be two written midterm exams, intended to be completed individual
without access to notes or documentation. The midterms are intended to achieve a learning
focus of reasoning about data structures in isolation from coding environments,
as well provide me as an instructor with greater insight into how effective course
instruction has been.
\bigskip
\noindent I will provide practice midterms one week prior to the exam date, and we will go over the practice midterm in the class prior to the exam date.

\subsubsection*{Final Project}

Feedback will be provided on the final project. The final project will be considered when determining grades for this course.

There will be a final project that will be similar in format but distinct in content from
homeworks. Whereas homeworks will including programming assignments for which there is
some correct answer that may be measured against an answer key and notions of coding
style, the project will be a student-centered exploration of data structures meant to
give you an opportunity to apply what you've learned in the course while still receiving
support from an instructor.

\bigskip
\noindent The final project will be released as soon as the final homework is due
 and will be due at the time of the final examination as set 
by the registrar.

\subsection*{Feedback and Grading}
Feedback will be provided on assignments, midterms, and the final project using a 100 point scale.
This 100 point scale is intended to be familiar to established grading standards, such as letter grades. To provide aggregate feedback for the whole course, these feedback scores will be combined as follows:
\begin{itemize}
	\item \underline{\textbf{40\%}} of your grade will be determined by homework assignments
	\item \underline{\textbf{40\%}} of your grade will be determined by midterm exams.
	\subitem \underline{\textbf{20\%}} each for the two midterms.
	\item \underline{\textbf{20\%}} of your grade will be determined by the final project.
\end{itemize}

If you receive a higher score on the second midterm than the first term, the second midterm's score will replace the first midterm's score.

\noindent Feedback scores will constitute the minimum grade on an assignment, but the instructor
may exercise discretion at any time to award a higher grade. For example, a submitted homework
may not use some important algorithmic technique as submitted, but if the student showed familiarity
with this technique on an earlier assignment or exam, the absence of that technique in a specific
case need not be counted against a student in grading, but only noted in feedback. This corresponds to the high level notion of feedback corresponding to how well an assignment reached the intended learning goals, while the overall course grade is meant to indicate that a student is prepared to succeed in latter coursework. Under this model, the final project will offer an opportunity to show familiarity with all content in the course, so a strong final project can ensure a high course grade
for any student, regardless of prior scores on midterms and homeworks.

\input{college}

\end{document}

